---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figure/"
)
```

# deconvolve

The R package *deconvolve* provides tools for performing non-parametric 
deconvolution on measurement error problems. It contains functions for finding 
bandwidths, deconvolved densities and non-parametric regression estimates.

## Installation

You can install the **development** version from 
[Github](https://github.com/timothyhyndman/deconvolve).

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("timothyhyndman/deconvolve")
```

## Usage

```{r, eval=FALSE}
library(deconvolve)
W <- (framingham$SBP21 + framingham$SBP22)/2
d <- deconvolve(W)

```

## Available methods
This is a list of every method that this package contains

##### Deconvolution
- Homoscedastic errors estimated from replicates
- Heteroscedastic errors estimated from replicates
- Errors assumed symmetric when no errors are provided
- Homoscedastic errors supplied
- Heteroscedastic errors supplied

##### Bandwidth selection
- Plug-in estimator for homoscedastic errors estimated from replicates
- Plug-in estimator for errors assumed symmetric when no errors are provided
- Plug-in estimator for homoscedastic errors
- Plug-in estimator for heteroscedastic errors
- CV for homoscedastic errors
- SIMEX for homoscedastic errors
- SIMEX for homoscedastic errors estimated from replicates

##### Regression
- Homoscedastic errors estimated from replicates
- Homoscedastic errors supplied


## License

This package is free and open source software, licensed under GPL (>=2).
